---
title: "A UN Report on Relationship Between GDP and Life Expectancy"
author: "Moses Mutua"
output: html_document
date: "2025-10-14"
---

```{r packages, include=FALSE}
library(tidyverse)
library(knitr)
```

# Introduction

Lorem ipsum, text example for this space including current text.

```{r data, include=FALSE}
gapminder_1997 <- 
  read.csv("gapminder_1997.csv")

nCountries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()

minGDP <- gapminder_1997 %>%
  summarize(round(min(gdpPercap))) %>%
  pull()

maxGDP <- gapminder_1997 %>%
  summarize(round(max(gdpPercap))) %>%
  pull()

```
### Summary
The above plot shows the relationship between GDP per capita and life expectancy for a total of `r nCountries` countries. For this set of countries, economic wealth ranged from a minimum of USD `r minGDP` to a maximum of `r maxGDP`per capita.

|Summary of Data|
|----------|----------|
|Number of Countries|`r nCountries`|
|Minimum GDP per capita|`r minGDP`|
|Maximum GDP per capita| `r maxGDP`|

# Data

```{r tables, echo=FALSE}
gapminder_1997 %>%
  filter(continent == "Americas") %>%
  kable()

```


```{r gdp_lifeexp_1997, echo=FALSE}
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap,
      y = lifeExp,
      color = continent,
      size = pop/1000000) +
  geom_point() +
  labs(x = "GDP per Capita",
       y = "Life Expectancy",
       title = "Do people in wealthy countries live longer?",
       size = "Population (millions)")
```


1. **MATLAB**
2. *ggplot*
3. ***Mathematical modeling***
4. <a href="https://gist.github.com/musleh0001/e3811443d5c793f1a8d5691e888d9632">[Markdown Cheat Sheet] #Markdown</a>
5. [[Markdown Cheat Sheet] #Markdown](https://gist.github.com/musleh0001/e3811443d5c793f1a8d5691e888d9632)